---
title: "myMonopolyQuarto"
format: html
editor: visual
---

# myMonopoly v.1

The goal of this project is to simulate Monopoly in R in order to see if Georgist rules outperform the regular rules in tax-dollars collected and in the fairness of the game (measured in how slowly the game reaches a state of monopoly).

## Game Logic

Player Movement, Functions

```{r}
X11()
source("boardGraphics.R")
source("gameBoardData.R")

## Player A Starting Position, GO!-point coordinates
#points(gameBoard$XtileCoordinate[1], 
#       gameBoard$YtileCoordinate[1],
#       type = "p",
#       pch = 16,
#       col = player_A_data$color)

## Player B Starting Position, GO!-point coordinates
#points(gameBoard$XtileCoordinate[1], 
#       gameBoard$YtileCoordinate[1],
#       type = "p",
#       pch = 16,
#       col = player_B_data$color)

#### Dice Function ####
dice <- function(n_dice){
  dice_res <- sample(1:6, n_dice)
  dice_res <- sum(dice_res)
  return(dice_res)
}

#### Player Movement Function ####
movePlayer <- function(player_Data){
  roll <- dice(2)
  updatePos <- player_Data$position + roll
  
  points(gameBoard$XtileCoordinate[player_Data$position], 
         gameBoard$YtileCoordinate[player_Data$position],
         type = "p",
         pch = 16,
         col = "white")
  points(gameBoard$XtileCoordinate[updatePos], 
         gameBoard$YtileCoordinate[updatePos],
         type = "p",
         pch = 16,
         col = player_Data$color) 
  player_Data$position <- updatePos
  if (player_Data$position > 40){
    points(gameBoard$XtileCoordinate[(player_Data$position - updatePos)], 
           gameBoard$YtileCoordinate[(player_Data$position - updatePos)],
           type = "p",
           pch = 16,
           col = "white")
    player_Data$position <- player_Data$position - 40
    points(gameBoard$XtileCoordinate[player_Data$position], 
           gameBoard$YtileCoordinate[player_Data$position],
           type = "p",
           pch = 16,
           col = player_Data$color) 
    print("New GO!")
    player_Data$money <- player_Data$money + 200
    moveList <- list(player_Data)
    return(moveList)
  } else {
    moveList <- list(player_Data)
    return(moveList)
  }
}
```

Chance, Function

```{r}
chanceFunc <- function(player_Data){
  dice_sum <- dice(3)
  chanceEvents_DF <- data.frame(
    c(3:18), 
    c("3#? Get out of jail-card.",
      "4#? Pay speeding ticket.",
      "5#? Street maintenance. 40 kr/house, 40 kr/hotel.",
      "6#? Property repair. 25 kr/house, 100kr/hotel.",
      "7#? Crossword price.",
      "8#? Go to Pennsylvania Stat. If pass GO, reap reward.",
      "9#? Go to JAIL!",
      "10#? Go to Illinois Av. If pass GO, take reward.",
      "11#? Payment on buildingloan.",
      "12#? Back three steps.",
      "13#? Go to GO!",
      "14#? Go to Boardwalk.",
      "15#? Go to St. Charles Place. If pass GO, reap reward.",
      "16#? Pay kindergarten fee.",
      "17#? Pay insider fine.",
      "18#? Gather savings interest.")
    )

  if (dice_sum == 3){
    next
  } else if (dice_sum == 4){
    player_Data$money <- player_Data$money - 15
  } else if (dice_sum == 5){
    # 5#? Street maintenance. 40 kr/house, 40 kr/hotel.
    houses <- sum(
      c(sum(gameBoard$propCurrentPlayer == "1"), 
        sum(gameBoard$propCurrentPlayer == "2"),
        sum(gameBoard$propCurrentPlayer == "3"),
        sum(gameBoard$propCurrentPlayer == "4")
        )
      )
    hotels <- sum(
      sum(gameBoard$propCurrentPlayer == "H") 
      )
    streetBill <- houses*40 + hotels*40
    print("streetBill:")
    print(streetBill)
    player_Data$money <- player_Data$money - streetBill
    
  } else if (dice_sum == 6){
    # 6#? Property repair. 25 kr/house, 100kr/hotel."
    houses <- sum(
      c(sum(gameBoard$propCurrentPlayer == "1"), 
        sum(gameBoard$propCurrentPlayer == "2"),
        sum(gameBoard$propCurrentPlayer == "3"),
        sum(gameBoard$propCurrentPlayer == "4")
        )
      )
    hotels <- sum(
      sum(gameBoard$propCurrentPlayer == "H") 
      )
    repairBill <- houses*25 + hotels*100
    print("repairBill:")
    print(repairBill)
    player_Data$money <- player_Data$money - repairBill
    
  } else if (dice_sum == 7){
    player_Data$money <- player_Data$money + 100
  } else if (dice_sum == 8){
    if (player_Data$position < 15){
      player_Data$position <- 15
    } else {
      player_Data$money <- player_Data$money + 200
      player_Data$position <- 15
    }
  } else if (dice_sum == 9){
    player_Data$position <- 11
  } else if (dice_sum == 10){
    if (player_Data$position < 25){
      player_Data$position <- 25
    } else {
      player_Data$money <- player_Data$money + 200
      player_Data$position <- 25
    }
  } else if (dice_sum == 11){
    player_Data$money <- player_Data$money + 150
  } else if (dice_sum == 12){
    player_Data$position <- player_Data$position - 3
  } else if (dice_sum == 13){
    player_Data$position <- 1
  } else if (dice_sum == 14){
    player_Data$position <- 40
  } else if (dice_sum == 15){
    if (player_Data$position < 12){
      player_Data$position <- 12
    } else {
      player_Data$money <- player_Data$money + 200
      player_Data$position <- 12
    }
  } else if (dice_sum == 16){
    player_Data$money <- player_Data$money - 150
  } else if (dice_sum == 17){
    player_Data$money <- player_Data$money - 20
  } else {
    player_Data$money <- player_Data$money + 50
  }
  
  event <- chanceEvents_DF[dice_sum, 2]
  chanceEventList <- list(player_Data, dice_sum, event)
  return(chanceEventList)
}
```

Community Chest, Function

```{r}
communityChestFunc <- function(player_Data){
  dice_sum <- dice(3)
  communityEvents_DF <- data.frame(
    c(3:18), 
    c("3#CC Get out of jail-card.",
      "4#CC Dentistpay.",
      "5#CC Pre-sold stock return.",
      "6#CC Mis-calc in your favour.",
      "7#CC Second-place in pageant.",
      "8#CC Divy on taxes.",
      "9#CC Go to JAIL!",
      "10#CC Pay insurance-premium.",
      "11#CC Annuity expires.",
      "12#CC Inheritance.",
      "13#CC Go to GO!",
      "14#CC Go to Mediterranean Av.",
      "15#CC Dividend on preference shares.",
      "16#CC Pay 10 kr in fines or chanse.",
      "17#CC Happy birthday! Take 10 kr / player.",
      "18#CC Private doctor fee.")
    )

  if (dice_sum == 3){
    next
  } else if (dice_sum == 4){
    player_Data$money <- player_Data$money - 100
  } else if (dice_sum == 5){
    player_Data$money <- player_Data$money + 50
  } else if (dice_sum == 6){
    player_Data$money <- player_Data$money + 200
  } else if (dice_sum == 7){
    player_Data$money <- player_Data$money + 10
  } else if (dice_sum == 8){
    player_Data$money <- player_Data$money + 20
  } else if (dice_sum == 9){
    player_Data$position <- 11
  } else if (dice_sum == 10){
    player_Data$money <- player_Data$money - 50
  } else if (dice_sum == 11){
    player_Data$money <- player_Data$money + 100
  } else if (dice_sum == 12){
    player_Data$money <- player_Data$money + 100
  } else if (dice_sum == 13){
    player_Data$position <- 1
  } else if (dice_sum == 14){
    player_Data$position <- 2
  } else if (dice_sum == 15){
    player_Data$money <- player_Data$money + 25
  } else if (dice_sum == 16){
    res <- rbinom(1, 1, 0.5)
    if (res == 0){
      player_Data$money <- player_Data$money - 10
    } else {
      randomEventFunc(player_Data$position, player_Data)
    }
  } else if (dice_sum == 17){
    player_Data$money <- player_Data$money + 10
  } else {
    player_Data$money <- player_Data$money - 50
  }
  
  event <- communityEvents_DF[dice_sum, 2]
  CCEventList <- list(player_Data, dice_sum, event)
  return(CCEventList)
}
```

Draw Houses, Function

```{r}
drawHousesFunc <- function(player_Data){
  houseMoney <- player_Data$money
  
  houseCost <- data.frame(
    colors = c("brown", "cyan", "magenta", "orange", 
               "red", "yellow", "green", "blue"),
    cost = c(50, 50, 100, 100, 150, 150, 200, 200)
  )
  #print("#=#")
  #print(player_Data$position)
  #print(gameBoard$tileType[player_Data$position])
  #print("1")
  #print(which(houseCost$colors == gameBoard$tileType[player_Data$position]))
  #print("2")
  #print(houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])])
  
  if (gameBoard$tileNr[player_Data$position] <= 11) {
          
          if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("0","1")) == T) == T 
              & 
              player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
              &
              gameBoard$propCurrentPlayer[player_Data$position] == "0"
              ) {
            
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "1", 
              col = "green", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "1"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
    
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("1","2")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "1"
                     )
                     {
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "1", 
              col = player_Data$color, 
              cex = 0.95, 
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "2", 
              col = "green", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "2"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("2","3")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "2"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "2", 
              col = player_Data$color, 
              cex = 0.95, 
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "3", 
              col = "green", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "3"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("3","4")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "3"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "3", 
              col = player_Data$color, 
              cex = 0.95, 
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "4", 
              col = "green", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "4"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
            
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("4","H")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "4"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "4", 
              col = player_Data$color, 
              cex = 0.95, 
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] + 0.035, 
              "H", 
              col = "red", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "H"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          }
    
          
        } else if (gameBoard$tileNr[player_Data$position] >= 12 
             & 
             gameBoard$tileNr[player_Data$position]<= 21) {
          
          if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("0","1")) == T) == T   
              & 
              player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
              &
              gameBoard$propCurrentPlayer[player_Data$position] == "0"
              ) {
            
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "1", 
              col = "green", 
              cex = 0.95, 
              srt = 90
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "1"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("1","2")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "1"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "1", 
              col = player_Data$color, 
              cex = 0.95, 
              srt = 90
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "2", 
              col = "green", 
              cex = 0.95, 
              srt = 90
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "2"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("2","3")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "2"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "2", 
              col = player_Data$color, 
              cex = 0.95, 
              srt = 90
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "3", 
              col = "green", 
              cex = 0.95, 
              srt = 90
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "3"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("3","4")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "3"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "3", 
              col = player_Data$color, 
              cex = 0.95, 
              srt = 90
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "4", 
              col = "green", 
              cex = 0.95, 
              srt = 90
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "4"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("4","H")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "4"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "4", 
              col = player_Data$color, 
              cex = 0.95, 
              srt = 90
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position] + 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "H", 
              col = "red", 
              cex = 0.95, 
              srt = 90
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "H"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          }
          
        } else if (gameBoard$tileNr[player_Data$position] >= 21 
             & 
             gameBoard$tileNr[player_Data$position]<= 31) {
          
          if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("0","1")) == T) == T 
              & 
              player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
              &
              gameBoard$propCurrentPlayer[player_Data$position] == "0"
              ) {
            
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "1", 
              col = "green", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "1"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("1","2")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "1"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "1", 
              col = player_Data$color, 
              cex = 0.95, 
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "2", 
              col = "green", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "2"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("2","3")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "2"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "2", 
              col = player_Data$color, 
              cex = 0.95, 
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "3", 
              col = "green", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "3"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("3","4")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "3"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "3", 
              col = player_Data$color, 
              cex = 0.95, 
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "4", 
              col = "green", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "4"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("4","H")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "4"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "4", 
              col = player_Data$color, 
              cex = 0.95, 
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position], 
              gameBoard$YtileCoordinate[player_Data$position] - 0.035, 
              "H", 
              col = "red", 
              cex = 0.95, 
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "H"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          }
          
        } else {
          
          if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("0","1")) == T) == T  
              & 
              player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
              &
              gameBoard$propCurrentPlayer[player_Data$position] == "0"
              ) {
            
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "1", 
              col = "green", 
              cex = 0.95, 
              srt = 270
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "1"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("1","2")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "1"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "1", 
              col = player_Data$color, 
              cex = 0.95, 
              srt = 270
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "2", 
              col = "green", 
              cex = 0.95, 
              srt = 270
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "2"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("2","3")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "2"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "2", 
              col = player_Data$color, 
              cex = 0.95, 
              srt = 270
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "3", 
              col = "green", 
              cex = 0.95, 
              srt = 270
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "3"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("3","4")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "3"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "3", 
              col = player_Data$color, 
              cex = 0.95, 
              srt = 270
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "4", 
              col = "green", 
              cex = 0.95, 
              srt = 270
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "4"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          } else if (all((gameBoard$propCurrentPlayer[which(gameBoard$tileType == gameBoard$tileType[player_Data$position])] %in% c("4","H")) == T) == T 
                     & 
                     player_Data$money >= houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
                     &
                     gameBoard$propCurrentPlayer[player_Data$position] == "4"
                     ) {
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "4", 
              col = player_Data$color, 
              cex = 0.95, 
              srt = 270
              )
            text(
              gameBoard$XtileCoordinate[player_Data$position] - 0.035, 
              gameBoard$YtileCoordinate[player_Data$position], 
              "H", 
              col = "red", 
              cex = 0.95, 
              srt = 270
              )
            gameBoard$propCurrentPlayer[player_Data$position] <<- "H"
            houseMoney <- player_Data$money -
      houseCost$cost[which(houseCost$colors == gameBoard$tileType[player_Data$position])]
            return(houseMoney)
          
          }
          
        }
  return(houseMoney)
}
```

Buy Tile, Function

```{r}
buyTileFunction <- function(player_Data, ownedColors){
      ## Player Buy Tiles, Graphics [START] ##
if (gameBoard$ownedBy[player_Data$position] == "none" 
    &
    player_Data$money >= gameBoard$tileCost[player_Data$position]){
  
      print("Action: buy.")
      text(
        1.2, 
        0.85, 
        "Action: buy.", 
        col = player_Data$color, 
        cex = 0.95, 
      )
      
      a <- masterTileList[[player_Data$position]][1]
      b <- masterTileList[[player_Data$position]][2]
      
      if (gameBoard$tileNr[player_Data$position] <= 11) {
        polygon(
          c(a[[1]][1], 
            a[[1]][3], 
            a[[1]][2],
            a[[1]][4]),
        
          c(b[[1]][1],
            b[[1]][2],
            b[[1]][3], 
            b[[1]][4]),
        
            col = player_Data$color,
            border = "black"
          )
        
      } else if (gameBoard$tileNr[player_Data$position] >= 12 
             & 
             gameBoard$tileNr[player_Data$position]<= 21) {
        polygon(
          c(a[[1]][4], 
            a[[1]][1], 
            a[[1]][2],
            a[[1]][3]),
      
          c(b[[1]][2],
            b[[1]][4],
            b[[1]][3], 
            b[[1]][1]),
      
          col = player_Data$color,
          border = "black"
          )
    
      } else if (gameBoard$tileNr[player_Data$position] >= 21 
             & 
             gameBoard$tileNr[player_Data$position]<= 31) {
        polygon(
          c(a[[1]][1], 
            a[[1]][3], 
            a[[1]][2],
            a[[1]][4]),
      
          c(b[[1]][1],
            b[[1]][2],
            b[[1]][3], 
            b[[1]][4]),
      
          col = player_Data$color,
          border = "black"
          )
    
      } else {
        polygon(
          c(a[[1]][4], 
            a[[1]][1], 
            a[[1]][2],
            a[[1]][3]),
      
          c(b[[1]][2],
            b[[1]][4],
            b[[1]][3], 
            b[[1]][1]),
      
          col = player_Data$color,
          border = "black"
        )
        }
  
      player_Data$money <- player_Data$money -
      gameBoard$tileCost[player_Data$position]
  
      gameBoard$ownedBy[player_Data$position] <<- player_Data$name
      ## Player Buy Tile, Graphics [END]    ##
      
      ## Player Buy Housing, Graphics [START] ##
      } else if (
        sum(gameBoard$tileType[gameBoard$ownedBy == player_Data$name] 
        == gameBoard$tileType[player_Data$position]) == 3 
        || 
        sum(gameBoard$tileType[gameBoard$ownedBy == player_Data$name] 
        == gameBoard$tileType[player_Data$position]) == 2 && 
        "brown" %in% gameBoard$tileType[player_Data$position] 
        || 
        sum(gameBoard$tileType[gameBoard$ownedBy == player_Data$name] 
        == gameBoard$tileType[player_Data$position]) == 2 && 
        "blue" %in% gameBoard$tileType[player_Data$position]
        ){
        
        cat("You got a full colour group in;",    
        gameBoard$tileType[player_Data$position])
        
        ownedColors$ownedBy[which(ownedColors$colors %in% gameBoard$tileType[player_Data$position])] <- player_Data$name
        
        player_Data$money <- drawHousesFunc(player_Data)
        
      } else {
        print("Action: too expensive.")
        text(
          1.2, 
          0.85, 
          "Action: too expensive.", 
          col = player_Data$color, 
          cex = 0.95, 
        )
      }
      ## Player Buy Housing, Graphics [END] ##
  buyOutputList <- list(player_Data, ownedColors)
  return(buyOutputList)
}
```

Mortage Flip, Function

```{r}
mortageFlipFunction <- function(player_Data, ownedColors){
  
  ## Mortage Flip, Graphics [START] ##
  posibleMortage <- gameBoard$mortageIncome[gameBoard$ownedBy 
                                       == player_Data$morgageStamp]
  
  affordableMortage <- player_Data$money >= posibleMortage
  
  gameBoard$ownedBy[gameBoard$mortageIncome == posibleMortage[max(affordableMortage)]] <<- player_Data$name
  player_Data$money <- player_Data$money - posibleMortage[max(affordableMortage)]
  ## Mortage Flip, Graphics [END] ##
  
  positionProxy_all <- gameBoard$tileNr[gameBoard$mortageIncome == posibleMortage[max(affordableMortage)]]
  print(positionProxy_all) #
  print(positionProxy_all[1]) #
  positionProxy <- positionProxy_all[1]

  ## Player Buy Tiles, Graphics [START] ##
  if (positionProxy >= 0){
    
        print("Action: buy.")
        text(
          1.2, 
          0.85, 
          "Action: buy.", 
          col = player_Data$color, 
          cex = 0.95, 
        )
        
        a <- masterTileList[[positionProxy]][1]
        b <- masterTileList[[positionProxy]][2]
        
        if (gameBoard$tileNr[positionProxy] <= 11) {
          polygon(
            c(a[[1]][1], 
              a[[1]][3], 
              a[[1]][2],
              a[[1]][4]),
          
            c(b[[1]][1],
              b[[1]][2],
              b[[1]][3], 
              b[[1]][4]),
          
              col = player_Data$color,
              border = "black"
            )
          
        } else if (gameBoard$tileNr[positionProxy] >= 12 
               & 
               gameBoard$tileNr[positionProxy]<= 21) {
          polygon(
            c(a[[1]][4], 
              a[[1]][1], 
              a[[1]][2],
              a[[1]][3]),
        
            c(b[[1]][2],
              b[[1]][4],
              b[[1]][3], 
              b[[1]][1]),
        
            col = player_Data$color,
            border = "black"
            )
      
        } else if (gameBoard$tileNr[positionProxy] >= 21 
               & 
               gameBoard$tileNr[positionProxy]<= 31) {
          polygon(
            c(a[[1]][1], 
              a[[1]][3], 
              a[[1]][2],
              a[[1]][4]),
        
            c(b[[1]][1],
              b[[1]][2],
              b[[1]][3], 
              b[[1]][4]),
        
            col = player_Data$color,
            border = "black"
            )
      
        } else {
          polygon(
            c(a[[1]][4], 
              a[[1]][1], 
              a[[1]][2],
              a[[1]][3]),
        
            c(b[[1]][2],
              b[[1]][4],
              b[[1]][3], 
              b[[1]][1]),
        
            col = player_Data$color,
            border = "black"
          )
          }
    
        gameBoard$ownedBy[positionProxy] <<- player_Data$name
  ## Player Buy Tile, Graphics [END]    ##
        
        } else if (
          sum(gameBoard$tileType[gameBoard$ownedBy == player_Data$name] 
          == gameBoard$tileType[positionProxy]) == 3 
          || 
          sum(gameBoard$tileType[gameBoard$ownedBy == player_Data$name] 
          == gameBoard$tileType[positionProxy]) == 2 && 
          "brown" %in% gameBoard$tileType[positionProxy] 
          || 
          sum(gameBoard$tileType[gameBoard$ownedBy == player_Data$name] 
          == gameBoard$tileType[positionProxy]) == 2 && 
          "blue" %in% gameBoard$tileType[positionProxy]
          ){
          
          cat("You got a full colour group in;",    
          gameBoard$tileType[positionProxy])
          
          ownedColors$ownedBy[which(ownedColors$colors %in% gameBoard$tileType[positionProxy])] <<- player_Data$name
           }
  
  mortageFlipOut <- list(player_Data, ownedColors)
  return(mortageFlipOut)
}
```

Sell Tile, Function

```{r}
sellTileFunction <- function(player_Data, ownedColors, i){
  ## Player Sell Tile, Graphics [START] ##
if (player_Data$money < 0 & 
      sum((gameBoard$ownedBy == player_Data$name),
          na.rm = T) < 1) {
    
    print("You are broke! (1)")
    print("You have no assets to sell. Game Over!")
    print(" -(1)- ")
    i <- 500
    gameOver <<- 1 # For two player game loop
    sellOutputList <- list(player_Data$position, player_Data, ownedColors, i)
    return(sellOutputList) # Trying to make game end when -(1)- happens.
    
  } else if (player_Data$money < 0 & 
      sum(
        (ownedColors$ownedBy == player_Data$name), 
        na.rm = T) < 1) {
    
    print("You are broke! (2)")
    print("You have assets to sell.")
  
    sellOrKeep <- which(gameBoard$ownedBy %in% player_Data$name)
    mortageThis <- which(gameBoard$tileCost[sellOrKeep] == min(gameBoard$tileCost[sellOrKeep]))
    
    gameBoard$ownedBy[sellOrKeep[mortageThis[1]]] <<- player_Data$morgageStamp

    ownedColors$ownedBy[which(ownedColors$colors %in% gameBoard$tileType[sellOrKeep[mortageThis[1]]])] <- NA

    # animate #
    a <- masterTileList[[sellOrKeep[mortageThis[1]]]][1]
    b <- masterTileList[[sellOrKeep[mortageThis[1]]]][2]
    
    if (sellOrKeep[mortageThis[1]] <= 11) {
      polygon(
        c(a[[1]][1], 
          a[[1]][3], 
          a[[1]][2],
          a[[1]][4]),
      
        c(b[[1]][1],
          b[[1]][2],
          b[[1]][3], 
          b[[1]][4]),
      
          col = player_Data$color,
          border = "white",
          lwd = 2, 
          lty = "dashed"
          )
      
    } else if (sellOrKeep[mortageThis[1]] >= 12 
           & 
           sellOrKeep[mortageThis[1]]<= 21) {
      polygon(
        c(a[[1]][4], 
          a[[1]][1], 
          a[[1]][2],
          a[[1]][3]),
    
        c(b[[1]][2],
          b[[1]][4],
          b[[1]][3], 
          b[[1]][1]),
    
          col = player_Data$color,
          border = "white",
          lwd = 2, 
          lty = "dashed"
          )
  
    } else if (sellOrKeep[mortageThis[1]] >= 21 
           & 
           sellOrKeep[mortageThis[1]]<= 31) {
      polygon(
        c(a[[1]][1], 
          a[[1]][3], 
          a[[1]][2],
          a[[1]][4]),
    
        c(b[[1]][1],
          b[[1]][2],
          b[[1]][3], 
          b[[1]][4]),
    
          col = player_Data$color,
          border = "white",
          lwd = 2, 
          lty = "dashed"
          )
  
    } else {
      polygon(
        c(a[[1]][4], 
          a[[1]][1], 
          a[[1]][2],
          a[[1]][3]),
    
        c(b[[1]][2],
          b[[1]][4],
          b[[1]][3], 
          b[[1]][1]),
    
          col = player_Data$color,
          border = "white",
          lwd = 2, 
          lty = "dashed"
          )
      }
    # ======= #
    
    print(player_Data$money)
    player_Data$money <- player_Data$money + gameBoard$mortageIncome[sellOrKeep[mortageThis[1]]]
    print(player_Data$money)
    print(" -(2)- ")
      
  } else if (player_Data$money < 0
             &
             sum(
        (ownedColors$ownedBy == player_Data$name), 
        na.rm = T) >= 1 
             ){
    
    print("You are broke! (3)")
    print("You have assets to sell, dont ruin your color monopoly!")
    
    playerMonopolys <- ownedColors$ownedBy == player_Data$name

    ownedTiles <- gameBoard$tileType[gameBoard$ownedBy == player_Data$name]

    maybeMorgage <- ownedTiles[((ownedTiles %in% ownedColors$colors[playerMonopolys]) == F)]

    maybeMorgagePrice <- gameBoard$mortageIncome[gameBoard$tileType %in% maybeMorgage]

    mortageTile <- which(gameBoard$tileNr == (which(gameBoard$mortageIncome == min(maybeMorgagePrice))))

    if (length(maybeMorgage) == 0){
      print("All your assets are monopolys. You have to sell of some houses or tiles from an ubuilt monopoly!")
      # Add code for when this happens - although it rarely happens. It might happen more often when I add counter players demanding rent.
      print(" -(3_A)- ")
    } else {
      print("Some of your assets are not monopolys. You can sell one of those tiles!")
      gameBoard$ownedBy[mortageTile[1]] <<- player_Data$morgageStamp
      
      ownedColors$ownedBy[which(ownedColors$colors %in%(gameBoard$tileType[mortageTile[1]]))] <- NA
      
    # animate #
    a <- masterTileList[[mortageTile[1]]][1]
    b <- masterTileList[[mortageTile[1]]][2]
    
    if (mortageTile <= 11) {
      polygon(
        c(a[[1]][1], 
          a[[1]][3], 
          a[[1]][2],
          a[[1]][4]),
      
        c(b[[1]][1],
          b[[1]][2],
          b[[1]][3], 
          b[[1]][4]),
      
          col = player_Data$color,
          border = "white",
          lwd = 2, 
          lty = "dashed"
          )
      
    } else if (mortageTile >= 12 
           & 
           mortageTile <= 21) {
      polygon(
        c(a[[1]][4], 
          a[[1]][1], 
          a[[1]][2],
          a[[1]][3]),
    
        c(b[[1]][2],
          b[[1]][4],
          b[[1]][3], 
          b[[1]][1]),
    
          col = player_Data$color,
          border = "white",
          lwd = 2, 
          lty = "dashed"
          )
  
    } else if (mortageTile >= 21 
           & 
           mortageTile <= 31) {
      polygon(
        c(a[[1]][1], 
          a[[1]][3], 
          a[[1]][2],
          a[[1]][4]),
    
        c(b[[1]][1],
          b[[1]][2],
          b[[1]][3], 
          b[[1]][4]),
    
          col = player_Data$color,
          border = "white",
          lwd = 2, 
          lty = "dashed"
          )
  
    } else {
      polygon(
        c(a[[1]][4], 
          a[[1]][1], 
          a[[1]][2],
          a[[1]][3]),
    
        c(b[[1]][2],
          b[[1]][4],
          b[[1]][3], 
          b[[1]][1]),
    
          col = player_Data$color,
          border = "white",
          lwd = 2, 
          lty = "dashed"
          )
      }
    # ======= #

    print(player_Data$money)
    player_Data$money <- player_Data$money + gameBoard$mortageIncome[mortageTile]
    print(player_Data$money)

    print(" -(3_B)- ")
    }
    
  } else {
    print("Continue...")
    print(player_Data$money)
  }
## Player Sell Tile, Graphics [END] ##
  sellOutputList <- list(player_Data, ownedColors, i)
  return(sellOutputList)
}
```

Game Loop

```{r}
#### Game Loop ####
gameLoop <- function(framePause, 
                     n_loops, 
                     player_Data,
                     roundNr) {
  
  ## Data Colecting [START] ##
  #visited_tiles <- c()
  ts_balance <- c()
  ## Data Colecting [END] ##
  
  ownedColors <- data.frame(
    colors = c("brown", "cyan", "magenta", "orange", 
               "red", "yellow", "green", "blue"),
    ownedBy = c(NA, NA, NA, NA, NA, NA, NA, NA)
  )
  
  for (i in 1:n_loops) {
    
    ## Simulation Readout, Console [START] ##
    print(
    c("tileNr:" = gameBoard$tileNr[player_Data$position], 
      "tileType:" = gameBoard$tileType[player_Data$position], 
      "ownedBy:" = gameBoard$ownedBy[player_Data$position],
      "player money:" = player_Data$money)
    )
    ## Simulation Readout, Console [END] ##
    
    ## Game Stats, Graphics [START] ##
    text(
      0.74, 
      0.8, 
      "'roundNr':", 
      col = "black", 
      cex = 0.95, 
    )
    text(
      0.84, 
      0.8, 
      roundNr, 
      col = "blue", 
      cex = 0.95, 
    )
    ## Game Stats, Graphics [END] ##
    
    ## Player Stats, Graphics [START] ## 
    text(
      1.05, 
      0.8, 
      "'tileNr':", 
      col = player_Data$color, 
      cex = 0.95, 
    )
    text(
      1.11, 
      0.8, 
      gameBoard$tileNr[player_Data$position], 
      col = "blue", 
      cex = 0.95, 
    )
    
    text(
      1.2, 
      0.8, 
      "'tileType':", 
      col = player_Data$color, 
      cex = 0.95, 
    )
    text(
      1.32, 
      0.8, 
      gameBoard$tileType[player_Data$position], 
      col = "blue", 
      cex = 0.95, 
    )
    
    text(
      1.08, 
      0.76, 
      "'ownedBy':", 
      col = player_Data$color, 
      cex = 0.95, 
    )
    text(
      1.2, 
      0.76, 
      gameBoard$ownedBy[player_Data$position], 
      col = "blue", 
      cex = 0.95, 
    )
    
    text(
      1.3, 
      0.76, 
      player_Data$money, 
      col = "darkgreen", 
      cex = 0.95, 
    )
    text(
      1.38, 
      0.76, 
      "$", 
      col = "darkgreen", 
      cex = 0.95, 
    )
    
    if (gameBoard$tileType[player_Data$position] == "I") {
      player_Data$money <- player_Data$money - 200
      print("Action: pay income tax.")
      text(
        1.2, 
        0.90,
        "Action: pay income tax.", 
        col = player_Data$color, 
        cex = 0.95, 
      )
    } else if (gameBoard$tileType[player_Data$position] == "S") {
      player_Data$money <- player_Data$money - 100
      print("Action: pay super tax.")
      text(
        1.2, 
        0.90,
        "Action: pay super tax.", 
        col = player_Data$color, 
        cex = 0.95, 
      )
    } else if (gameBoard$tileType[player_Data$position] == "CC"){
      randCC <- communityChestFunc(player_Data)
      # update player #
      points(gameBoard$XtileCoordinate[player_Data$position], 
             gameBoard$YtileCoordinate[player_Data$position],
             type = "p",
             pch = 16,
             col = "white")

      player_Data <- randCC[[1]]
      dice_sum <- randCC[[2]]
      event <- randCC[[3]]
      print(event)
      text(
        1.2, 
        0.90,
        paste0("CC#:", dice_sum), 
        col = player_Data$color, 
        cex = 0.95, 
      )
      
    } else if (gameBoard$tileType[player_Data$position] == "?"){
      randChance <- chanceFunc(player_Data)
      # update player #
      points(gameBoard$XtileCoordinate[player_Data$position], 
             gameBoard$YtileCoordinate[player_Data$position],
             type = "p",
             pch = 16,
             col = "white")

      player_Data <- randChance[[1]]
      dice_sum <- randChance[[2]]
      event <- randChance[[3]]
      print(event)
      text(
        1.2, 
        0.90,
        paste0("?#:", dice_sum), 
        col = player_Data$color, 
        cex = 0.95, 
      )
      
    } else if (gameBoard$tileType[player_Data$position] == "GT_J") {
      print("Action: go to jail!")
      text(
        1.2, 
        0.90,
        "Action: go to jail!", 
        col = player_Data$color, 
        cex = 0.95, 
      )
      points(gameBoard$XtileCoordinate[player_Data$position], 
             gameBoard$YtileCoordinate[player_Data$position],
             type = "p",
             pch = 16,
             col = "white")
      player_Data$position <- 11
      points(gameBoard$XtileCoordinate[player_Data$position], 
             gameBoard$YtileCoordinate[player_Data$position],
             type = "p",
             pch = 16,
             col = player_Data$color)
    ## Player Stats, Graphics [END] ##
    } else if ( gameBoard$ownedBy[player_Data$position] 
                %in% 
                c("!", "none", player_Data$name, player_Data$morgageStamp) == F){
      print("Action: pay rent to other player!")
      print(gameBoard$ownedBy[player_Data$position])
      
      # update player #
      points(gameBoard$XtileCoordinate[player_Data$position], 
             gameBoard$YtileCoordinate[player_Data$position],
             type = "p",
             pch = 16,
             col = "white")
      text(
        1.2, 
        0.90,
        "Action: pay rent to other player!", 
        col = player_Data$color, 
        cex = 0.95, 
      )
      ################
      
      if (gameBoard$propCurrentPlayer[player_Data$position] 
          == "0"){
        
        print("0 houses.")
        
        player_Data$money <- player_Data$money - gameBoard$tileRent[player_Data$position]
      player_Data$debtCounter <- gameBoard$tileRent[player_Data$position]
      player_Data$debtorName <- gameBoard$ownedBy[player_Data$position]
      
      } else if (gameBoard$propCurrentPlayer[player_Data$position] 
                 == "1"){
        
        print("1 house.")
        
        player_Data$money <- player_Data$money - gameBoard$house_1_Cost[player_Data$position]
      player_Data$debtCounter <- gameBoard$house_1_Cost[player_Data$position]
      player_Data$debtorName <- gameBoard$ownedBy[player_Data$position]
      
      } else if (gameBoard$propCurrentPlayer[player_Data$position] 
                 == "2"){
        
        print("2 houses.")
        
        player_Data$money <- player_Data$money - gameBoard$house_2_Cost[player_Data$position]
      player_Data$debtCounter <- gameBoard$house_2_Cost[player_Data$position]
      player_Data$debtorName <- gameBoard$ownedBy[player_Data$position]
      
      } else if (gameBoard$propCurrentPlayer[player_Data$position] 
                 == "3"){
        
        print("3 houses.")
        
        player_Data$money <- player_Data$money - gameBoard$house_3_Cost[player_Data$position]
      player_Data$debtCounter <- gameBoard$house_3_Cost[player_Data$position]
      player_Data$debtorName <- gameBoard$ownedBy[player_Data$position]
      
      } else if (gameBoard$propCurrentPlayer[player_Data$position] 
                 == "4"){
        
        print("4 houses.")
        
        player_Data$money <- player_Data$money - gameBoard$house_4_Cost[player_Data$position]
      player_Data$debtCounter <- gameBoard$house_4_Cost[player_Data$position]
      player_Data$debtorName <- gameBoard$ownedBy[player_Data$position]
      
      } else if (gameBoard$propCurrentPlayer[player_Data$position] 
                 == "H"){
        
        print("A hotel.")
        
        player_Data$money <- player_Data$money - gameBoard$house_hotel_Cost[player_Data$position]
      player_Data$debtCounter <- gameBoard$house_hotel_Cost[player_Data$position]
      player_Data$debtorName <- gameBoard$ownedBy[player_Data$position]
      
      }
        
      print(gameBoard$tileRent[player_Data$position])
    }
    
    ## Player Buy Tiles, Graphics [START] ##
    buyOutput <- buyTileFunction(player_Data, ownedColors)
    player_Data <- buyOutput[[1]]
    ownedColors <- buyOutput[[2]]
    
    while ( any(gameBoard$ownedBy == player_Data$morgageStamp) == T
            &
            any( player_Data$money > gameBoard$mortageIncome[gameBoard$ownedBy == player_Data$morgageStamp] ) == T
  ){
      print("Mortaged tiles to buy!")

      mortageFlipOutput <- mortageFlipFunction(player_Data, 
                                               ownedColors
                                               )

      player_Data <- mortageFlipOutput[[1]]
      ownedColors <- mortageFlipOutput[[2]]
    }
    print("NO mortaged tiles to buy.")
    ## Player Buy Tile, Graphics [END]    ##
      
    ## Player Sell Tile, Graphics [START] ##
    while (player_Data$money < 0){
      sellOutput <- sellTileFunction(player_Data, 
                                     ownedColors,
                                     i
                                     )

      player_Data <- sellOutput[[1]]
      ownedColors <- sellOutput[[2]]
      i <- sellOutput[[3]] # Trying to end game when Game Over.
      print(player_Data$money)
    }
    ## Player Sell Tile, Graphics [END]   ##
    
    Sys.sleep(framePause)
    
    # clear Stat Graphics #
    polygon(
    c(0.68, 0.89, 0.89, 0.68), 
    c(0.95, 0.95, 0.725, 0.725),
    col = "white",
    border = "white"
    )
    
    polygon(
    c(1, 1.4, 1.4, 1), 
    c(0.95, 0.95, 0.725, 0.725),
    col = "white",
    border = "white"
    )
    
    ## Data Collecting [START] ##
    #visited_tiles <- append(visited_tiles, player_Data$position)
    ts_balance <- append(ts_balance, player_Data$money)
    ## Data Collecting [END] ##
    
    # update player #
    movePlayer_Output <- movePlayer(player_Data)
    player_Data <- movePlayer_Output[[1]]
    print(player_Data)
  }
  ## Print and Return Data [START] ##
  print("Printing dfSimOutput, current Player:")
  n_rounds <- roundNr #length(visited_tiles)
  #dfSimOutput <- data.frame(
                    #visited_tiles = table(visited_tiles,
                    #                      dnn = "TileNr")
                    #)
  outputList <- list(
                     "n_rounds" = n_rounds, 
                     "ts_balance" = ts_balance,
                     "player_Data" = player_Data,
                     "visited_tiles" = n_rounds
                     )
  return(outputList)
  ## Print and Return Data [END] ##
}

```

Simulation Settings

```{r}
X11() # sets the default device to X11 for plotting in a sperate window
source("boardGraphics.R")
source("gameBoardData.R")

#### gameLoop Inputs ####
framePause <- 0.25
n_loops <- 1 # 500
playerA_Col <- "purple1"
playerB_Col <- "tan"
#tilePos <- 1

#### Player A Data ####
player_A_data <- data.frame(
  "name" = "player_A",
  "money" = 1500,
  "color" = "purple1", # playerA_Col
  "morgageStamp" = "morgaged_A",
  "position" = 1,
  "debtCounter" = 0,
  "debtorName" = "none"
)

#### Player B Data ####
player_B_data <- data.frame(
  "name" = "player_B",
  "money" = 1500,
  "color" = "tan", # playerB_Col
  "morgageStamp" = "morgaged_B",
  "position" = 1,
  "debtCounter" = 0,
  "debtorName" = "none"
)

#### Simulation Results ####
#myRecord <- gameLoop(framePause, 
                     #player_Col = playerA_Col, 
                     #n_loops = n_loops, 
                     #player_Data = player_A_data,
                     #tilePos = tilePos)
#myRecord

#### Two player Loop ####
player_1 <- player_A_data
player_2 <- player_B_data
currentPlayer <- player_1
gameOver <- 0
visited_tiles <- 0

while (gameOver == 0) {
  
  visited_tiles <- visited_tiles + 1
  print("####")
  print(visited_tiles)
  print("####")
  print(currentPlayer$name)
  print("####")
  if (visited_tiles %% 2 == 0) {
    myRecord <- gameLoop(framePause, 
                       n_loops, 
                       player_Data = currentPlayer,
                       roundNr = visited_tiles)
    player_2 <- myRecord$player_Data
    
    player_2$money <- player_2$money + player_1$debtCounter
    player_2$debtCounter <- 0
    player_2$debtorName <- "none"
    
    currentPlayer <- player_1
    print("# IF #")
    print(currentPlayer$name)
    print("##")
  } else {
    myRecord <- gameLoop(framePause, 
                       n_loops, 
                       player_Data = currentPlayer,
                       roundNr = visited_tiles)
    player_1 <- myRecord$player_Data
    
    player_1$money <- player_1$money + player_2$debtCounter
    player_1$debtCounter <- 0
    player_1$debtorName <- "none"
    
    currentPlayer <- player_2
    print("# ELSE #")
    print(currentPlayer$name)
    print("##")
  }
}

```

Debugging

```{r}
print("Debugging empty.")
```
